Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2015-09-12 3dpas_intro.tex
refinement.

  A common feature across many science and engineering applications is the
  amount and diversity of data and computation that must be integrated to yield
  insights. Often data is increasingly large-scale and distributed. Often the
  datasets, their locations, availability, analysis and associated scheduling
  decisions are time-dependent. Collectively these give rise to dynamic
  distributed data intensive applications. This paper attempts to survey several
  such applications, to provide a common conceptual framework to understand them
  as well as examine the infrastructure used in support of applications.
  Whereas the analysis of large volumes of ``static'' data have received
  significant attention, the ability to manage large-volumes of dynamic and
  distributed data is more primitive. This work will ameliorate the state.

>>>>

  A common feature across many science and engineering applications is the
  amount and diversity of data and computation that must be integrated to yield
  insights. Often data is increasingly large-scale and distributed. Often the
  datasets, their locations, availability, analysis and associated scheduling
  decisions are time-dependent. Collectively these give rise to dynamic
  distributed data intensive applications.  The characteristics, requirements,
  and software systems for the analysis of large volumes of ``static'' data have
  received significant attention; dynamic, distributed and data intensive (3D)
  have received relatively less. This work will ameliorate the state by
  surveying several representative 3D application scenarios, to provide a common
  conceptual framework to understand them as well as examine the infrastructure
  used in support of applications.
